\subsection{Devops}
Nowadays, in digital business, we offer and delivery wide range of services through digital experiences and to improve these services we have to have the feedback from the customer to start being able to deliver new types of experiences and values. Doing this, we are going to be more competitive and interact with the customer in new ways, something that all industries are going through.
All these, we can arrive just doing with good practices to do the work far far more efficient. Here we enter in the DevOps World.

DevOps is primely  about the culture, collaborative practices and automation that aligns Development and Operation teams so that they have a single mindset on improving customer experiences, responding faster to business needs, and ensuring that innovation is balanced with security and operational needs \cite{IsaacSacolick2016DrivingCulture}. This means:

\begin{itemize}
\item Automate testing.
\item Ensure more frequent and reliable deployments.
\item Develop clarity on roles and responsibilities.
\item Define Key Performance Indicator \(KPI\) and scopes.
\item Automating and monitoring.
\end{itemize}

To start this concept, we have to make sure the people are aligned with what DevOps is, and with a challenge and not with the whole set of DevOps practices.

Also, we have to keep the focus in QA knowing that it is a distinct discipline and skill set, but should work with Dev to develop and automate test case.

\paragraph{Participant}
% https://youtu.be/eMSrjr5vyoI 24min PARTe de organizacion
\subparagraph{Dev}
QUe es Dev y q deberia hacer
%https://youtu.be/q01IjipC-8o Digital Driving

\subparagraph{Ops}
QUe es Ops y q deberia hacer

\subsection{Continues everyone}
%https://youtu.be/oGX8DB9aZb0
no podemos automanizar todo, como devops es tambien una cultura, y cultura incluye a las personas, no podemos automatizar a las personas.
Son las personas
